### 2016-12-22 analysis-note-vf/results.tex
update the analysis note with the latest plots for both DVCS channels

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.72]{fig_updated/f_coh_alu_Q2_phi.pdf} 
\includegraphics[scale=0.72]{fig_updated/f_coh_alu_xB_phi.pdf}
\includegraphics[scale=0.72]{fig_updated/f_coh_alu_t_phi.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
   represent the statistical and the systematic uncertainties, added 
quadratically, shown on the top of green error bars representing only the 
statistical uncertainties. The brown bands represent the full systematic 
uncertainties, including the normalisation systematic uncertainties. The red 
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

@@

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.37]{fig_ch5/coh_alu_Q2_90.png} \\
\includegraphics[scale=0.37]{fig_ch5/coh_alu_xB_90.png} \\
\includegraphics[scale=0.37]{fig_ch5/coh_alu_t_90.png} 
\caption{The $Q^{2}$-dependence (on the top), the $x_{B}$-dependence (on the 
   middle), and the $t$-dependence~(on the bottom) of the fitted coherent 
   $A_{LU}$ signals at $\phi$= 90$^{\circ}$ (black squares). On the middle: the red and the 
   blue curves are theoretical predictions from \cite{simonetta_2} at two 
values of $-t$. On the bottom: the green circles are the HERMES $-A_{LU}$ 
(positron beam was used) inclusive measurements \cite{HERMES_BSA}, and the 
colored curves represent theoretical predictions from \cite{simonetta_2}.} 
\label{fig:coh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[tpb]
\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_Q2_phi.pdf}
\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_xB_phi.pdf}
\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_t_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ function.  
} \label{fig:bsa_incoh_bins}
\end{figure}

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf}\\ 
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \\ 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
the colored curves represent theoretical calculations from \cite{simonetta_2}.  
} \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[h!]
\hspace{-0.5in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_Q2.pdf}
\hspace{-0.3in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_xB.pdf}
\centering \includegraphics[scale=0.38]{fig_updated/f_coh_cff_t.pdf}
\caption{The model-independent extraction of the imaginary (blue points) and 
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_t.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S. 
Liuti and K. Taneja \cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_xB.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_t.pdf}
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results of 
   this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}

>>>>

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_phi.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
   represent the statistical and the systematic uncertainties, added 
   quadratically, shown on the top of green error bars representing only the 
statistical uncertainties.  The brown bands represent the full systematic 
uncertainties, including the normalisation systematic uncertainties. The red 
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

@@

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_phi_90.pdf}
   \caption{The $Q^{2}$-dependence (on the top), the $x_{B}$-dependence (on the 
      middle), and the $t$-dependence~(on the bottom) of the fitted coherent 
      $A_{LU}$ signals at $\phi$= 90$^{\circ}$ (black squares). On the middle: 
      the red and the blue curves are theoretical predictions from 
      \cite{simonetta_2} at two values of $-t$. On the bottom: the green 
      circles are the HERMES $-A_{LU}$ (positron beam was used) inclusive 
      measurements \cite{HERMES_BSA}, and the colored curves represent 
      theoretical predictions from \cite{simonetta_2}.} 
      \label{fig:coh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[tpb]
\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_Q2.pdf}
\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_x.pdf}
\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_t.pdf}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
   figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
   represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ 
   function.  } \label{fig:bsa_incoh_bins}
\end{figure}

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_Q2_shortscenrario.pdf}\\ 
\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_x_shortscenrario.pdf}\\
\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_t_shortscenrario.pdf} \\ 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
   $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
   the colored curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (blue points) and 
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S. 
Liuti and K. Taneja \cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_ratio.pdf}\\
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results 
   of this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
   blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
